---
title: "FWSAkRDRtools Tutorial"
output:
  knitr:::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{mdJSONdictio}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  markdown:
    wrap: sentence
---

```{=html}
<style type="text/css">
  body{
  font-size: 12pt;
}
</style>
```
```{css, echo=FALSE}
# .main-container {
#     max-width: 600px !important;
# }

pre {
  max-height: 350px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
pre code {
  white-space: pre
}
```

# Workspace

## Uninstall

Run the following to uninstall FWSAkRDRtools.

```{r, eval=FALSE}
remove.packages("FWSAkRDRtools")
.rs.restartR()
```

## Install

Run the following to install the development version of FWSAkRDRtools.
If you already have an older version of FWSAkRDRtools installed in your library, run the code above to uninstall before proceeding.

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")

Sys.setenv(R_REMOTES_STANDALONE="true")
remotes::install_github("hdvincelette/FWSAkRDRtools")

```

## Load

Run setup code.

```{r setup, eval=FALSE}
options(width = 9999)

knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  error=TRUE
)

```

Load FWSAkRDRtools into the library and set the working directory (where you would like files to be saved and/or copied from).

```{r, eval=FALSE}
library(FWSAkRDRtools)

wd<- "C:/Users/hvincelette/OneDrive - DOI/Documents/Data_management/Test"

```

# Functions

## `get.dir.template()`

```{r, eval=FALSE}

get.dir.template(
  project = "mbmlb_909_Eskimo_Curlew_study",
  local.path = wd,
  main = TRUE,
  incoming = FALSE
)

```

## `clone.project()`

```{r, eval=FALSE}

clone.project(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  local.path = wd,
  main = TRUE,
  incoming = TRUE
  )

```

## `find.files()`

```{r, eval=FALSE}

find.files(
  pattern = c("template", "dictionary", "\\.csv", "hello"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "metadata",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  full.path = FALSE
)

```

## `download.files()`

```{r, eval=FALSE}

download.files(
  pattern = c("banding", "dictionary"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "",
  local.path = wd,
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  download.file.method = "auto"
)

```

## `read.tables()`

```{r, eval=FALSE}

df <- read.tables(
  pattern = c("dictionary"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "metadata",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  header = TRUE,
  na.strings = ""
)

df.list <- read.tables(
  pattern = c("\\.csv", "\\.xlsx"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  header = TRUE,
  na.strings = ""
)

```

## `summarize.files()`

```{r, eval=FALSE}

file.summary<- summarize.files(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder = "",
  main = TRUE,
  incoming = TRUE,
  recursive = TRUE
)
```

## `commit.files()`

```{r, eval=FALSE}
# Note files will only be committed if you are the data steward of the project. Refer to the Data Manager to understand your project roles.

commit.summary<- commit.files(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  local.path = paste0(wd,"/mbmlb_010_Grey_headed_chickadee_hybridization"),
  recursive = TRUE
  )

```
