---
title: "FWSAkRDRtools Tutorial"
output:
  knitr:::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{mdJSONdictio}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  markdown:
    wrap: sentence
---

```{=html}
<style type="text/css">
  body{
  font-size: 12pt;
}

</style>
```
```{css, echo=FALSE}
# .main-container {
#     max-width: 600px !important;
# }

pre {
  max-height: 350px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
pre code {
  white-space: pre
}
```

The 'FWSAkRDRtools' R package is meant to help users access and manage files on the U.S.
Fish & Wildlife Service Alaska Regional Data Repository (RDR).
The RDR is a "network drive serving as a central location for authoritative project data and deliverables".
Currently, the RDR is internally maintained and can only be accessed by FWS employees connected to the Service’s network onsite or through approved remote connection technologies, such as a [Virtual Private Network (VPN)](https://doimspp.sharepoint.com/sites/fws-FF10T00000/SitePages/GlobalProtect-Secure-Technology-Application.aspx).
Connected users can navigate to the RDR by pasting the link <file://ifw7ro-file.fws.doi.net/datamgt/> in File Explorer or a web browser (e.g., Microsoft Edge or Chrome) (Figure 1).
Please refer to the [Draft Regional Data Repository Guidance Document](https://ecos.fws.gov/ServCat/Reference/Profile/150400) on ServCat for more information on the overall organization and management of the RDR.
Most 'FWSAkRDRtools' functions require an FWS network connection, and one function also requires write permission to the relevant 'incoming' project folder (Table 1).

```{r, echo = FALSE, out.width = "50%", out.height = "20%", fig.cap = "Figure 1. *The Alaska Regional Data Repository in File Explorer (left) and Microsoft Edge (right).*", fig.show = 'hold', fig.align = 'left'}
knitr::include_graphics(
  c(
    "https://github.com/hdvincelette/FWSAkRDRtools/raw/main/vignettes/images/RDR_file_explorer.png",
    "https://github.com/hdvincelette/FWSAkRDRtools/raw/main/vignettes/images/RDR_web_browser.png"
  )
)

```

# Workspace

## Uninstall

If you have installed 'FWSAkRDRtools' previously and want to update to the latest version, you may need to uninstall the package first.
Occasionally R hits a roadblock and needs you to manually remove a package before it can proceed.

```{r, eval=FALSE}
remove.packages("FWSAkRDRtools")
.rs.restartR()
```

## Install

Install the development version of 'FWSAkRDRtools' from GitHub.
The R package 'remotes' (demonstrated here) or 'devtools' is required to install packages from GitHub.

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")

Sys.setenv(R_REMOTES_STANDALONE="true")
remotes::install_github("hdvincelette/FWSAkRDRtools")

```

## Load

Run the following housekeeping code to set chunk behavior within this document.

```{r setup, eval=FALSE}
options(width = 9999)

knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  error=TRUE
)

```

Load 'FWSAkRDRtools' into the R library and set the working directory (where you would like files to be saved and/or copied from).

```{r, eval=FALSE}
library(FWSAkRDRtools)

wd<- "C:/Users/hvincelette/OneDrive - DOI/Documents/Data_management/Test"

```

Run the following to access information about 'FWSAkRDRtools' in the Help pane, including documentation pages for each function.
You can use this as a quick reference for function usage, arguments, and expected output.

```{r}

help(package = "FWSAkRDRtools")

```

# Functions

## `get.dir.template()`: get the directory tree template

Connection to the FWS network is *not* required.

```{r, eval=FALSE}

get.dir.template(
  project = "mbmlb_909_Eskimo_Curlew_study",
  local.path = wd,
  main = TRUE,
  incoming = FALSE
)

```

## `find.projects()`: find RDR projects

Requirements:

-   none

```{r, eval=FALSE}

find.projects(pattern = c("red.*knot","alaska"), program = "mbm", full.path = FALSE)

```

## `find.files()`: find RDR project files

Requirements:

-   connection to the FWS network

-   write access to the applicable RDR project "incoming" folder (i.e., Data Steward or Data Manager)

```{r, eval=FALSE}

find.files(
  pattern = c("template", "dictionary", "\\.csv", "hello"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "metadata",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  full.path = FALSE
)

```

## `download.files()`: download RDR project files

```{r, eval=FALSE}

download.files(
  pattern = c("banding", "dictionary"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "",
  local.path = wd,
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  download.file.method = "auto"
)

```

## `read.tables()`: read RDR project tables into R

```{r, eval=FALSE}

df <- read.tables(
  pattern = c("dictionary"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "metadata",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  header = TRUE,
  na.strings = ""
)

df.list <- read.tables(
  pattern = c("\\.csv", "\\.xlsx"),
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder.path = "",
  main = TRUE,
  incoming = FALSE,
  recursive = TRUE,
  header = TRUE,
  na.strings = ""
)

```

## `clone.project()`: clone an RDR project

```{r, eval=FALSE}

clone.project(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  local.path = wd,
  main = TRUE,
  incoming = TRUE
  )

```

## `summarize.files()`: summarize files in an RDR project

```{r, eval=FALSE}

file.summary<- summarize.files(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  subfolder = "",
  main = TRUE,
  incoming = TRUE,
  recursive = TRUE
)
```

## `commit.files()`: commit files to an RDR project

```{r, eval=FALSE}
# Note files will only be committed if you are the data steward of the project. Refer to the Data Manager to understand your project roles.

commit.summary<- commit.files(
  project = "mbmlb_010_Grey_headed_chickadee_hybridization",
  local.path = paste0(wd,"/mbmlb_010_Grey_headed_chickadee_hybridization"),
  recursive = TRUE
  )

```
